\sysfull

### 2018-08-07 paper/asplos19/paging.tex
Paging revised

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/coalesced-war.pdf}
	\caption{Task coalescing-induced WAR dependency (in the case of this example, at variable $x$). Such dynamic dependencies cannot be resolved at compile time and they break memory consistency.}
	\label{figure:coalescedWar}
\end{figure}

Resolving WAR (Write-After-Read) dependencies by considering static task boundaries is not sufficient to keep non-volatile memory consistent when tasks are coalesced. Not handling WAR dependencies with task coalescing introduces a new problem, which we denote as \emph{task coalescing-induced WAR dependency}. This problem is illustrated in Fig.~\ref{figure:coalescedWar}. Therefore, \sys implements novel {\em Virtual Memory Manager} (VMM) which enables task coalescing guaranteeing data integrity, which is at the same time efficient.

>>>>

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/coalesced-war.pdf}
	\caption{Task coalescing-induced WAR dependency (in the case of this example, at variable $x$). Such dynamic dependencies cannot be resolved at compile-time and they break memory consistency.}
	\label{figure:coalescedWar}
\end{figure}

Resolving WAR (Write-After-Read) dependencies by considering static task boundaries is not sufficient to keep non-volatile memory consistent when tasks are coalesced. Not handling WAR dependencies on a coalesced task scope introduces a new problem, which we denote as \emph{task coalescing-induced WAR dependency}. This problem is illustrated in Fig.~\ref{figure:coalescedWar}. Therefore, \sys implements novel {\em Virtual Memory Manager} (VMM) which enables task coalescing guaranteeing data integrity, which is at the same time efficient.
